---
title: "Analysis of PM 2.5 Air Quality in Los Angeles During Quarantine using CausalImpact and BSTS"
author: "Kenneth Foo"
date: "19/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis of PM 2.5 Air Quality in Los Angeles During Quarantine using CausalImpact and BSTS

With the recent COVID-19 pandemic, the implementation of quarantine and social distancing by various governments created a ripple of effects that affect cities all around the world. The key driver behind this was the halting of economic activity which brought about a big crunch in the global economy. In the early phase of the COVID-19 crisis, the media reported that [the carbon emissions in China was reduced drastically](https://www.nytimes.com/2020/02/26/climate/nyt-climate-newsletter-coronavirus.html) in mid Feb 2020.  This gave me an idea as I wanted to try out some time series analysis on air quality in certain cities with the implementation of a quarantine. 

I was always interested in learning the Bayesian Structured Time Series (BSTS) methodology for time series analysis, and had been doing some research on the `bsts` package. Going down the rabbit hole, I found another package called `CausalImpact` that was developed on top of the `bsts` package which allows for causal analysis of time series experiments. Although relatively unknown, both packages were developed by the smart guys working at Google. If you haven't heard about them, I highly encourage you to check them out.

In this article, I will be assessing the air quality of Los Angeles city and the impact of the quarantine. The following points frame my analysis:
- The type of air quality used for this analysis is the PM2.5, which stands for atmospheric particulate matter with a diameter of less than 2.5 micrometers. 
- The implementation of the quarantine will be perceived as an "intervention". The date of this intervention will be explained in more detail.
- Los Angeles was chosen because it is such an iconic city that is bustling with activity. Not only that, it is also know for its traffic congestion.

The data source taken 


```{r cars}
library(bsts)
library(CausalImpact)
library(tidyverse)
library(zoo)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
